The state of knowledge for marine invertebrate biodiversity in the continental US

### 2017-11-01 manuscript.Rmd
complete data + plot about kingdom stats

>>>>

```{r kingdom-stats}
get_vert_prop <- function(db) {
    format_output(kingdom_diversity[kingdom_diversity$database == db & kingdom_diversity$sub_kingdom == "Animalia - Vertebrates", "prop_spp"] * 100)
}

total_vert_prop <- get_vert_prop("worms")
idigbio_vert_prop <- get_vert_prop("idigbio")
obis_vert_prop <- get_vert_prop("obis")
```

Marine invertebrates are underrepresented in iDigBio and OBIS. We compared the total number of species represented in iDigBio and OBIS for each kingdom to the total described diversity based on the numbers published by WoRMS. Records in thedatabases are biased towards vertebrates: while vertebrates represent  `r total_vert_prop`% of the global diversity, they represent `r idigbio_vert_prop`% and `r obis_vert_prop`% of the records identified at the species level in iDigBio and OBIS respectively (Fig. \@ref(fig:kingdom-diversity-plot)). Additionally, the median number of specimen per species

```{r kingdom-diversity-plot, fig.cap='Comparison of the proportions of the diversity represented in iDigBio and OBIS  with the global diversity (as reported by WoRMS) for each kingdom. Vertebrates are overrepresented, while other animal groups are underpresented. Total number of species are indicated next to the bars.(\\#fig:kingdom-diversity-plot)'}
knitr::include_graphics("figures/plot_kingdom_diversity.pdf")
```
